---
title: "R Get the simulate_data"
author: "Helen Liu & Yikang Liu"
date: "16/05/2022"
output: html_document
---

This script is used to generate the "fake" data in stage 1 registration. We applied the Bootstrap methods where samples are drawn from the open data of Hu et al. (2020) (accessible at https://osf.io/mhdsn/, or in "2_2_1_refData" folder) with replacement (allowing the same sample to appear more than once in the fake data). 

Following the format of the secondary data, the fake data has 6 sessions of 34 participants’ data, where for each participant in each session, there are 24 practice trials and 360 experimental trials (six types of shape-label associations: two matches(matched/mismatched) x three shape associations, with 60 trials per association). 


```{r import used pacakge}
library(tidyverse)
library(here)
```

## set relative path

```{r, setup, include=FALSE}
# set working path
cur_dir <-  here::here()
knitr::opts_knit$set(root.dir = 'cur_dir')
```

## import reference data

```{r import reference data}
rsp_data = read_csv('../2_2_MaterialProc/2_2_1_refData/MS_rep_matchingTask_raw.csv') #reference of fake data 
```

## set parameters for simulation

```{r}
#set parameters
subjects = c(1:34) #34 subjects 
session = c(1:6)   #six sessions
matchness = c('Match','Nonmatch') # two matchness 
identity = c('Self','Friend','Stranger') # three identities
trialtype = c("prac","exp")# two trial types

ntrials = 78336 #total trials = nsubjects * nsessions * nmatchness * nidentities * (prac*4 + exp*60)
```

## create empty data frame

```{r}
# create empty data frame
dimnames = list(c(),c("Subject","Session","Matchness","Identity","Trialtype")) 
simdata = matrix(data = NA,
                 nrow = ntrials,
                 ncol = 5,
                 dimnames = dimnames)
```

## resample from reference data 

```{r}
#set parameters
nsamples = ntrials
replace = TRUE

#resample
set.seed(123)
RT = sample(x = rsp_data$RT, # the reference data
            size = nsamples, 
            replace = replace, #sampling with replacement
            prob = NULL)
ACC = sample(x = rsp_data$ACC, 
            size = nsamples, 
            replace = replace,
            prob = NULL)
```

## add the resampled rt & acc to the empty data frame

```{r}
RT = as.data.frame(RT)
simdata = cbind(simdata, RT)
ACC = as.data.frame(ACC)
simdata = cbind(simdata, ACC)
```

## add trial type

```{r}
set.seed(123)
for (i in c(1:ntrials)){
  if (i %% 64 == 1 | i %% 64 == 2 | i %% 64 == 3 | i %% 64 == 4){
    simdata$Trialtype[i] = 'prac'
  }else{
    simdata$Trialtype[i] = 'exp'
  }
} 
```

## add identity

```{r}
set.seed(123)
k = 0 # counter
for (i in c(1:ntrials)){
  k = k + 1 
  if (k <= 64){
    simdata$Identity[i] = 'Self'
  }else if(k >64 & k <= 128){
    simdata$Identity[i] = 'Friend'
  }else if(k >128 & k < 192){
    simdata$Identity[i] = 'Stranger'
  }else{
    simdata$Identity[i] = 'Stranger'
    k = 0
  }
} 
```

## add matchness

```{r}
set.seed(123)
k = 0
for (i in c(1:ntrials)){
  k = k + 1 
  if (k <= 192){
    simdata$Matchness[i] = 'Match'
  }else if(k >192 & k < 384){
    simdata$Matchness[i] = 'Nonmatch'
  }else{
    simdata$Matchness[i] = 'Nonmatch'
    k = 0
  }
} 
```

## add session

```{r}
set.seed(123)
k = 0
for (i in c(1:ntrials)){
  k = k + 1 
  if (k <= 384){
    simdata$Session[i] = 1
  }else if(k >384 & k <= 768){
    simdata$Session[i] = 2
  }else if(k >768 & k <= 1152){
    simdata$Session[i] = 3
  }else if(k >1152 & k <=1536 ){
    simdata$Session[i] = 4
  }else if(k >1536 & k <= 1920){
    simdata$Session[i] = 5
  }else if(k >1920 & k < 2304){
    simdata$Session[i] = 6
  }else{
    simdata$Session[i] = 6
    k = 0
  }
} 
```

## add subject_idx

```{r}
set.seed(123)
k = 0
for (i in c(0:33)){
  for (k in c(1:2304)) {
    simdata$Subject[2304*i + k] = i+1
  }
} 
```

## check simulated data structure

```{r}
View(simdata)
# check data structure
test <- simdata %>% 
  dplyr::group_by(Subject, Session, Matchness, Identity, Trialtype) %>% 
  dplyr::summarise(n=n())
test 
# check trial numbers in each condition
k<- 0 
w<- 0
for (i in c(1:2448)){
  if (test$n[i] !=4 & test$n[i] !=60){
    k = k+1
  }else{
    w = w+1
  }
}
k #we can see that the trial numbers are correct 
w

# check how many non&wrong-response trials we have 
sum(simdata$ACC == -1 |simdata$ACC == 2)
```

# save simulated data to local file

```{r}
###save simulated data to a local file
path_out = ("../2_3_SimData/") # define path out 
fileName = paste(path_out, 'simulated_data.csv', sep = '')
write_csv(simdata, fileName, col_names = TRUE, append = FALSE)
```

