---
title: "Untitled"
author: "yuki"
date: "2024-03-14"
output: html_document
---
Step 0: initial number of subjects

Step 1: filter subjects (mean_ACC < 0.5)
Step 2: drop subjects (mean_ACC < 0.5), write.csv
Step 3: read.csv

Step 1: double check the mean_ACC of subjects

```{r Step 0}
# 创建一个空列表来存储结果
subject_counts <- list()

# 循环遍历列表中的每个数据框
for (i in seq_along(df)) {
  # 计算当前数据框中不同的 Subject 的数量，并存储到结果列表中
  subject_counts[[i]] <- length(unique(df[[i]]$Subject))
}
```


# Check ACC
```{r Step 1, message=FALSE, warning=FALSE}
min_ACC_list <- list()

for (i in 1:length(df)) {
  min_ACC <- df[[i]] %>%
    dplyr::filter(Matching == "Matching") %>%
    dplyr::group_by(Subject) %>%
    #dplyr::group_by(Subject) %>%
    dplyr::summarise(mean_ACC = mean(ACC)) %>%
    dplyr::ungroup() %>%
    dplyr::filter(mean_ACC < 0.5) %>%
    dplyr::arrange(mean_ACC) %>%
    dplyr::distinct(Subject, .keep_all = TRUE)
  
  min_ACC_list[[i]] <- min_ACC
  cat(
    "For df[[", i, "]], the min ACC is:",
    min(min_ACC$mean_ACC),
    "\n"
  )
}

rm(min_ACC, min_ACC_list, i)
```

```{r Step 2}
for (i in 1:length(df)) {
  filtered_df <- df[[i]] %>%
    dplyr::anti_join(min_ACC_list[[i]], by = "Subject") 
  
  df[[i]] <- filtered_df
  
  write.csv(
    x = filtered_df,
    file = paste0("./DATA/df_", i, ".csv"),
    row.names = FALSE
  )
}

rm(filtered_df, i)
```


```{r Step 3}
# clean data r
df[[1]] <- read.csv("./DATA/df_1.csv")
df[[2]] <- read.csv("./DATA/df_2.csv")
df[[3]] <- read.csv("./DATA/df_3.csv")
df[[4]] <- read.csv("./DATA/df_4.csv")
df[[5]] <- read.csv("./DATA/df_5.csv")
df[[6]] <- read.csv("./DATA/df_6.csv")
df[[7]] <- read.csv("./DATA/df_7.csv")
df[[8]] <- read.csv("./DATA/df_8.csv")
df[[9]] <- read.csv("./DATA/df_9.csv")
df[[10]] <- read.csv("./DATA/df_10.csv")
df[[11]] <- read.csv("./DATA/df_11.csv")
df[[12]] <- read.csv("./DATA/df_12.csv")
df[[13]] <- read.csv("./DATA/df_13.csv")
df[[14]] <- read.csv("./DATA/df_14.csv")
df[[15]] <- read.csv("./DATA/df_15.csv")

# clean data s
df[[16]] <- read.csv("./DATA/df_16.csv")
df[[17]] <- read.csv("./DATA/df_17.csv")
df[[18]] <- read.csv("./DATA/df_18.csv")
df[[19]] <- read.csv("./DATA/df_19.csv")
df[[20]] <- read.csv("./DATA/df_20.csv")
df[[21]] <- read.csv("./DATA/df_21.csv")
df[[22]] <- read.csv("./DATA/df_22.csv")
df[[23]] <- read.csv("./DATA/df_23.csv")
df[[24]] <- read.csv("./DATA/df_24.csv")
df[[25]] <- read.csv("./DATA/df_25.csv")
df[[26]] <- read.csv("./DATA/df_26.csv")

# clean data t
df[[27]] <- read.csv("./DATA/df_27.csv")
df[[28]] <- read.csv("./DATA/df_28.csv")
df[[29]] <- read.csv("./DATA/df_29.csv")
df[[30]] <- read.csv("./DATA/df_30.csv")
df[[31]] <- read.csv("./DATA/df_31.csv")
df[[32]] <- read.csv("./DATA/df_32.csv")
df[[33]] <- read.csv("./DATA/df_33.csv")
df[[34]] <- read.csv("./DATA/df_34.csv")

# clean data u
df[[35]] <- read.csv("./DATA/df_35.csv")
df[[36]] <- read.csv("./DATA/df_36.csv")
df[[37]] <- read.csv("./DATA/df_37.csv")
df[[38]] <- read.csv("./DATA/df_38.csv")
df[[39]] <- read.csv("./DATA/df_39.csv")
df[[40]] <- read.csv("./DATA/df_40.csv")
df[[41]] <- read.csv("./DATA/df_41.csv")
df[[42]] <- read.csv("./DATA/df_42.csv")
df[[43]] <- read.csv("./DATA/df_43.csv")
df[[44]] <- read.csv("./DATA/df_44.csv")
df[[45]] <- read.csv("./DATA/df_45.csv")
```



