---
title: "Untitled"
author: "yuki"
date: "2024-03-25"
output: html_document
---
# Paper t10
## Experiment 1 (Identtiy = 2)
"Self", "Stranger"
```{r}
df[[35]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t10/Pt10_Exp1_raw.csv") %>%
  dplyr::filter(Procedure.SubTrial. == "BlockProcS") %>%
  dplyr::select(
    Subject,
    Label,
    Shape,
    ACC = TargetS.ACC,
    RT_ms = TargetS.RT,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Identity = case_when(
      Shape == "你" ~ "Self",
      Shape == "生人" ~ "Stranger",
    ),
    Matching = case_when(
      Shape == Label ~ "Matching",
      Shape != Label ~ "Nonmatching"),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[35] <- "Paper t10 Exp 1"
summary(df[[35]])
```


# Paper t18
## Experiment 1 (Identtiy = 3)
"Self", "Friend", "Stranger"
```{r}
df[[36]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t18/Pt18_Exp1_raw.csv") %>%
  dplyr::select(
    Subject = subj_idx,
    Identity = person,
    Matching = match,
    ACC = accuracy,
    RT_sec = rt,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Matching = case_when(
      Matching == "match" ~ "Matching",
      Matching == "mismatch" ~ "Nonmatching"),
    RT_sec = as.numeric(RT_sec),
    RT_ms = RT_sec * 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[36] <- "Paper t18 Exp 1"
summary(df[[36]])
```

# Paper 19
## Experiment 1 (Identtiy = 3)
"Self", "Friend", "Stranger"
```{r}
df[[37]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_19/P19_Exp1_raw.csv") %>%
  dplyr::filter(Session == 3) %>%
  dplyr::select(
    Subject,
    Session,
    Shape,
    Label,
    ACC = Target.ACC,
    RT_ms = Target.RT,
  ) %>%
  dplyr::mutate(
    Label = case_when(
      Label == "Sie" ~ "Self",
      Label == "Freund" ~ "Friend",
      Label == "Fremder" ~ "Stranger",
    ),
    Identity = Shape,
    Matching = case_when(
      Shape == Label ~ "Matching",
      Shape != Label ~ "Nonmatching",
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[37] <- "Paper 19 Exp 1"
summary(df[[37]])
```

# Paper 19
## Experiment 2 (Identtiy = 3)
"Self", "Friend", "Stranger"
```{r}
df[[38]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_19/P19_Exp2_raw.csv") %>%
  dplyr::filter(Session == 3) %>%
  dplyr::select(
    Subject,
    Session,
    Shape,
    Label,
    ACC = Target.ACC,
    RT_ms = Target.RT,
  ) %>%
  dplyr::mutate(
    Label = case_when(
      Label == "Sie" ~ "Self",
      Label == "Freund" ~ "Friend",
      Label == "Fremder" ~ "Stranger",
    ),
    Identity = Shape,
    Matching = case_when(
      Shape == Label ~ "Matching",
      Shape != Label ~ "Nonmatching",
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[38] <- "Paper 19 Exp 2"
summary(df[[38]])
```

# Paper 34
## Experiment 1 (Identtiy = 3)
"Self", "Friend", "Stranger"
```{r}
df[[39]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_34/P34_Exp1_raw_foracc.csv") %>%
  dplyr::filter(maincond == 1) %>% # delay = 0ms
  dplyr::select(
    Subject = subid,
    Identity = shape,
    Matching = matching,
    ACC = accuracy,
    RT_ms = reac_time,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Matching = case_when(
      Matching == 1 ~ "Matching",
      Matching == 0 ~ "Nonmatching",
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Identity = case_when(
      Identity == 1 ~ "Self",
      Identity == 2 ~ "Friend",
      Identity == 3 ~ "Stranger",
    ),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[39] <- "Paper 34 Exp 1"
summary(df[[39]])
```

# Paper 44
## Experiment 1 (Identtiy = 2)
"Self", "Friend", "Stranger"
```{r message=FALSE, warning=FALSE}
temp <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_44/P44_Exp1_raw.csv") %>%
  #dplyr::filter(Group == 5) # 5 = sham
  dplyr::select(
    Subject,
    Shape = Figura,
    Label = Etiqueta,
    Matching = TipoEnsayo,
    ACC = Blanco1.ACC,
    RT_ms = Blanco1.RT,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Matching = case_when(
      Matching == "Matched" ~ "Matching",
      Matching == "NonMatching" ~ "Nonmatching",
    ),
    Label = case_when(
      Label == "tu" ~ "Self",
      Label == "amigo" ~ "Friend",
      Label == "extrano" ~ "Stranger",
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) 
  

Subject_ID <- temp %>% # nolint
  dplyr::group_by(
    Subject
  ) %>%
  dplyr::summarise(
    count = n()
  ) %>%
  dplyr::mutate(
    Subject_ID = row_number()
  ) %>%
  dplyr::select(
    Subject, Subject_ID
  ) 

Correct <- temp %>%
  dplyr::filter(Matching == "Matching") %>%
  dplyr::group_by(
    Subject, Shape
  ) %>%
  dplyr::summarise(
    Identity = Label
  ) %>%
  dplyr::ungroup() %>%
  dplyr::distinct() %>%
  dplyr::right_join(
    Subject_ID,
    by = "Subject"
  )

df[[40]] <- temp %>%
  dplyr::left_join(
    Correct,
    by = c("Subject", "Shape")
  ) %>%
  dplyr::mutate(
    Subject = Subject_ID
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC,
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

rm(temp, Correct, Subject_ID)

names(df)[40] <- "Paper 44 Exp 1"
summary(df[[40]])
```

# Paper t27
## Experiment 2 (Identtiy = 3)
"Self", "Friend", "Stranger"
```{r message=FALSE, warning=FALSE}
temp <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t27/Pt27_Exp2_raw.csv") %>%
  dplyr::select(
    Subject,
    Shape = Figura,
    Label = Etiqueta,
    Matching = TipoEnsayo,
    ACC = Blanco1.ACC,
    RT_ms = Blanco1.RT,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Matching = case_when(
      Matching == "Matched" ~ "Matching",
      Matching == "NonMatching" ~ "Nonmatching",
    ),
    Label = case_when(
      Label == "tu" ~ "Self",
      Label == "amigo" ~ "Friend",
      Label == "extrano" ~ "Stranger",
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) 
  

Subject_ID <- temp %>% # nolint
  dplyr::group_by(
    Subject
  ) %>%
  dplyr::summarise(
    count = n()
  ) %>%
  dplyr::mutate(
    Subject_ID = row_number()
  ) %>%
  dplyr::select(
    Subject, Subject_ID
  ) 

Correct <- temp %>%
  dplyr::filter(Matching == "Matching") %>%
  dplyr::group_by(
    Subject, Shape
  ) %>%
  dplyr::summarise(
    Identity = Label
  ) %>%
  dplyr::ungroup() %>%
  dplyr::distinct() %>%
  dplyr::right_join(
    Subject_ID,
    by = "Subject"
  )

df[[41]] <- temp %>%
  dplyr::left_join(
    Correct,
    by = c("Subject", "Shape")
  ) %>%
  dplyr::mutate(
    Subject = Subject_ID
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

rm(temp, Correct, Subject_ID)

names(df)[41] <- "Paper t27 Exp 1"
summary(df[[41]])
```

# Paper t13
## Experiment 1 (Friend) (Identtiy = 2)
"Self", "Friend"
```{r}
temp <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t13/Pt13_Exp1a_raw.csv") %>%
  dplyr::filter(fill == "line") %>%
  dplyr::select(
    Subject = subject,
    Identity = Con_shape,
    Matching = Con_match,
    ACC = correct,
    RT_ms = latency,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Matching = case_when(
      Matching == "match" ~ "Matching",
      Matching == "unmatch" ~ "Nonmatching",
    ),
    Identity = case_when(
      Identity == "self" ~ "Self",
      Identity == "friend" ~ "Friend",
      Identity == "stranger" ~ "Stranger",
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) 
  

Subject_ID <- temp %>% # nolint
  dplyr::group_by(
    Subject
  ) %>%
  dplyr::summarise(
    count = n()
  ) %>%
  dplyr::mutate(
    Subject_ID = row_number()
  ) %>%
  dplyr::select(
    Subject, Subject_ID
  ) 

df[[42]] <- temp %>%
  dplyr::left_join(
    Subject_ID,
    by = "Subject"
  ) %>%
  dplyr::mutate(
    Subject = Subject_ID
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

rm(temp, Subject_ID)

names(df)[42] <- "Paper t13 Exp 1"
summary(df[[42]])
```

# Paper t13
## Experiment 2 (Stranger) (Identtiy = 2)
"Self", "Stranger"
```{r}
temp <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t13/Pt13_Exp1b_raw.csv") %>%
  dplyr::filter(fill == "line") %>%
  dplyr::select(
    Subject = subject,
    Identity = Con_shape,
    Matching = Con_match,
    ACC = correct,
    RT_ms = latency,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Matching = case_when(
      Matching == "match" ~ "Matching",
      Matching == "unmatch" ~ "Nonmatching",
    ),
    Identity = case_when(
      Identity == "self" ~ "Self",
      Identity == "friend" ~ "Friend",
      Identity == "stranger" ~ "Stranger",
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) 
  

Subject_ID <- temp %>% # nolint
  dplyr::group_by(
    Subject
  ) %>%
  dplyr::summarise(
    count = n()
  ) %>%
  dplyr::mutate(
    Subject_ID = row_number()
  ) %>%
  dplyr::select(
    Subject, Subject_ID
  ) 

df[[43]] <- temp %>%
  dplyr::left_join(
    Subject_ID,
    by = "Subject"
  ) %>%
  dplyr::mutate(
    Subject = Subject_ID
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

rm(temp, Subject_ID)

names(df)[43] <- "Paper t13 Exp 2"
summary(df[[43]])
```

# Paper t13
## Experiment 1 (Identtiy = 3)
```{r}
df[[44]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t28/Pt28_Exp1_raw.csv") %>%
  dplyr::filter(Subject < 50) %>% # non-ASD
  dplyr::select(
    Subject,
    Session,
    Label,
    Shape,
    ACC = Target.ACC,
    RT_ms = Target.RT,
  ) %>%
  dplyr::mutate(
    Label = case_when(
      Label == "Ikzelf" ~ "Self",
      Label == "Bekende" ~ "Friend",
      Label == "Vreemde" ~ "Stranger",
    ),
    Matching = case_when(
      Shape == Label ~ "Matching",
      Shape != Label ~ "Nonmatching",
    ),
    Identity = Shape,
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[44] <- "Paper t28 Exp 1"
summary(df[[44]])
```

# Paper t13
## Experiment 1 (Identtiy = 3)
```{r}
folder_path <- "../4_Data_Extraction/4_2_Open_Data/Paper_t7/Source/Raw/"

file_names <- list.files(folder_path, pattern = "*.csv", full.names = TRUE)

csv_list <- list()

for (i in seq_along(file_names)) {
  
  csv_data <- read.csv(file_names[i]) %>% 
    dplyr::mutate(Subject = i)
  
  csv_list[[i]] <- csv_data
}

combined_data <- dplyr::bind_rows(csv_list)

write.csv(
  x = combined_data, 
  file = "../4_Data_Extraction/4_2_Open_Data/Paper_t7/Pt7_Exp1_raw.csv",
  row.names = FALSE
)

rm(folder_path, csv_list, csv_data, combined_data)
```


```{r}
temp <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t7/Pt7_Exp1_raw.csv") %>%
  dplyr::filter(blockcode == "matchingStage") %>%
  dplyr::select(
    Subject,
    Matching = matchCondition,
    Identity = shapeCategory,
    ACC = correct,
    RT_ms = latency,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Identity = case_when(
      Identity == "self" ~ "Self",
      Identity == "friend" ~ "Friend",
      Identity == "stranger" ~ "Stranger",
    ),
    Matching = case_when(
      Matching == "match" ~ "Matching",
      Matching == "mismatch" ~ "Nonmatching",
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

df[[45]] <- temp

names(df)[45] <- "Paper t7 Exp 1"
summary(df[[45]])

rm(temp)
```

```{r}
df[[45]] <- temp %>%
  dplyr::filter(Subject <= 65)

df[[46]] <- temp %>%
  dplyr::filter(Subject > 65 & Subject <= 130)

df[[47]] <- temp %>%
  dplyr::filter(Subject > 130 & Subject <= 195)

df[[48]] <- temp %>%
  dplyr::filter(Subject > 195 & Subject <= 260)

df[[49]] <- temp %>%
  dplyr::filter(Subject > 260 & Subject <= 340)

rm(temp)

names(df)[45] <- "Paper t7 Exp 1a"
summary(df[[45]])

names(df)[46] <- "Paper t7 Exp 1b"
summary(df[[46]])

names(df)[47] <- "Paper t7 Exp 1c"
summary(df[[47]])

names(df)[48] <- "Paper t7 Exp 1d"
summary(df[[48]])

names(df)[49] <- "Paper t7 Exp 1e"
summary(df[[49]])
```


