---
title: "Untitled"
author: "yuki"
date: "2024-03-14"
output: html_document
---
# Paper t1 
## Experiment 1 (Identtiy = 2)
"Self", "Stranger"
```{r Paper t1 Experiment 1}
df[[27]] <- read.csv(
  "../4_Data_Extraction/4_2_Open_Data/Paper_t1/Pt1_Exp1_raw.csv"
  ) %>%
  dplyr::filter(
    Phase == 1,
  ) %>%
  dplyr::select(
    Subject,
    Matching = Condition,
    Identity = Target,
    RT_ms = WaitResponse.RT,
    ACC = IsCorrect,
  ) %>%
  dplyr::mutate(
    Identity = case_when(
      Identity == 1 ~ "Self",
      Identity == 2 ~ "Stranger",
    ),
    Matching = case_when(
      Matching == 1 ~ "Matching",
      Matching == 2 ~ "Nonmatching"
    ),
    Session = 1,
    ACC = case_when(
      ACC == "150" ~ 0,
      ACC == "151" ~ 1,
      ACC == "152" ~ NA,
    ),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[27] <- "Paper t1 Exp 1"
summary(df[[27]])
```

# Paper t2 
## Experiment 1 (Identtiy = 3)
"Self", "Friend", "Stranger"
```{r Paper t2 Experiment 1}
temp <- read.csv(
  "../4_Data_Extraction/4_2_Open_Data/Paper_t2/Pt2_Exp1_raw.csv"
  ) %>%
  dplyr::filter(
    Task == "Self",
  ) %>%
  dplyr::select(
    Subject = subject,
    # bug in R 4.1.3, the var name would be ï..subject
    Matching = Matching,
    Identity = Shape,
    RT_ms = mean_rt_mult,
    RT_sec = trial_resp.rt,
    ACC = acc,
  ) %>%
  dplyr::mutate(
    Matching = case_when(
      Matching == 1 ~ "Matching",
      Matching == 0 ~ "Nonmatching"
    ),
    Session = 1,
  ) 

Subject_ID <- temp %>% # nolint
  dplyr::group_by(
    Subject
  ) %>%
  dplyr::summarise(
    count = n()
  ) %>%
  dplyr::mutate(
    Subject_ID = row_number()
  ) %>%
  dplyr::select(
    Subject, Subject_ID
  )


df[[28]] <- temp %>%
  dplyr::left_join(
    Subject_ID,
    by = "Subject"
  ) %>%
  dplyr::mutate(
    Subject = Subject_ID
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

rm(temp, Subject_ID)

names(df)[28] <- "Paper t2 Exp 1"
summary(df[[28]])
```

# Paper t3 
## Experiment 1 (Identtiy = 2)
"Self", "Friend", "Stranger"
```{r Paper t3 Experiment 1}
df[[29]] <- read.csv(
  "../4_Data_Extraction/4_2_Open_Data/Paper_t3/Pt3_Exp1_raw.csv"
  ) %>%
  dplyr::filter(
    session == "pre",
  ) %>%
  dplyr::select(
    Subject = subj_idx,
    Matching = match,
    Identity = shape,
    RT_sec = rt,
    ACC = acc,
  ) %>%
  dplyr::mutate(
    Identity = case_when(
      Identity == "self" ~ "Self",
      Identity == "friend" ~ "Friend",
      Identity == "stranger" ~ "Stranger",
    ),
    Matching = case_when(
      Matching == 1 ~ "Matching",
      Matching == 0 ~ "Nonmatching"
    ),
    Session = 1,
    RT_sec = as.numeric(RT_sec),
    RT_ms = RT_sec * 1000
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[29] <- "Paper t3 Exp 1"
summary(df[[29]])
```

# Paper t6
## Experiment 1 (Identtiy = 2)
"Self", "Stranger"
```{r Paper t6 Experiment 1}
df[[30]] <- read.csv(
  "../4_Data_Extraction/4_2_Open_Data/Paper_t6/Pt6_Exp1_raw.csv"
  ) %>%
  dplyr::filter(block == "selfS") %>%
  dplyr::select(
    Subject = participant_id,
    Matching = match,
    Identity = shape,
    RT_sec = respRt,
    ACC = respCorr,
  ) %>%
  dplyr::mutate(
    Identity = case_when(
      Identity == "self-related" ~ "Self",
      Identity == "stranger-related" ~ "Stranger"
    ),
    Matching = case_when(
      Matching == "yes" ~ "Matching",
      Matching == "no" ~ "Nonmatching",
    ),
    ACC = case_when(
      ACC == 1 ~ 1,
      ACC == 0 ~ 0,
      ACC == "missed" ~ NA
    ),
    Session = 1,
    RT_sec = as.numeric(RT_sec),
    RT_ms = RT_sec * 1000
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[30] <- "Paper t6 Exp 1"
summary(df[[30]])
```

# Paper t6
## Experiment 2 (Identtiy = 2)
"Self", "Stranger"
```{r Paper t6 Experiment 2}
temp <- read.csv(
  "../4_Data_Extraction/4_2_Open_Data/Paper_t6/Pt6_Exp2_raw.csv"
  ) %>%
  dplyr::filter(block == "selfS") %>%
  dplyr::select(
    Subject = participant_id,
    Matching = match,
    Identity = shape,
    RT_sec = respRt,
    ACC = respCorr,
  ) %>%
  dplyr::mutate(
    Identity = case_when(
      Identity == "self-related" ~ "Self",
      Identity == "stranger-related" ~ "Stranger"
    ),
    Matching = case_when(
      Matching == "yes" ~ "Matching",
      Matching == "no" ~ "Nonmatching",
    ),
    ACC = case_when(
      ACC == 1 ~ 1,
      ACC == 0 ~ 0,
      ACC == "missed" ~ NA
    ),
    Session = 1,
    RT_sec = as.numeric(RT_sec),
    RT_ms = RT_sec * 1000
  ) 

Subject_ID <- temp %>% # nolint
  dplyr::group_by(
    Subject
  ) %>%
  dplyr::summarise(
    count = n()
  ) %>%
  dplyr::mutate(
    Subject_ID = row_number()
  ) %>%
  dplyr::select(
    Subject, Subject_ID
  )


df[[31]] <- temp %>%
  dplyr::left_join(
    Subject_ID,
    by = "Subject"
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject_ID),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Stranger")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[31] <- "Paper t6 Exp 2"
summary(df[[31]])
```

# Paper t9
## Experiment 1 (Identtiy = 3)
"Self", "Friend", "None"
```{r}
###############################Save Raw Data####################################
# 获取文件列表
file_list <- list.files(
  path = "../4_Data_Extraction/4_2_Open_Data/Paper_t9/Source/Data - Experiment 1/",
  pattern = "^SelfPriorExp_3.*\\.dat$",
  full.names = TRUE
)

# 读取dat文件并存入list中
data_list <- lapply(file_list, read.table, header = FALSE, sep = " ")

combined_data <- do.call(rbind, data_list)

write.csv(
  x = combined_data, 
  file = "../4_Data_Extraction/4_2_Open_Data/Paper_t9/Pt9_Exp1_raw.csv",
  row.names = FALSE
)

rm(file_list, data_list, combined_data)

##################################Clean Data####################################

df[[32]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t9/Pt9_Exp1_raw.csv") %>%
  dplyr::select(
    Subject = V1,
    Shape = V7,
    Label1 = V10,
    Label2 = V11,
    Label3 = V12,
    Matching = V14,
    ACC = V15,
    RT_ms = V16,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Shape = case_when(
      Shape == "shape1.jpg" ~ Label1,
      Shape == "shape2.jpg" ~ Label2,
      Shape == "shape3.jpg" ~ Label3,
    ),
    Identity = case_when(
      Shape == "You" ~ "Self",
      Shape == "none" ~ "None",
      TRUE ~ "Friend"
    ),
    Matching = case_when(
      Matching == 1 ~ "Matching",
      Matching == 2 ~ "Nonmatching"),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "None")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[32] <- "Paper t9 Exp 1"
summary(df[[32]])
```


# Paper t9
## Experiment 2 (Identtiy = 3)
"Self", "Friend", "None"
```{r}
###############################Save Raw Data####################################
# 获取文件列表
file_list <- list.files(
  path = "../4_Data_Extraction/4_2_Open_Data/Paper_t9/Source/Data - Experiment 2/",
  pattern = "^SelfPriorExp_1.*\\.dat$",
  full.names = TRUE
)

# 读取dat文件并存入list中
data_list <- lapply(file_list, read.table, header = FALSE, sep = " ")

combined_data <- do.call(rbind, data_list)

write.csv(
  x = combined_data, 
  file = "../4_Data_Extraction/4_2_Open_Data/Paper_t9/Pt9_Exp2_raw.csv",
  row.names = FALSE
)

rm(file_list, data_list, combined_data)

##################################Clean Data####################################

df[[33]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t9/Pt9_Exp2_raw.csv") %>%
  dplyr::select(
    Subject = V1,
    Shape = V7,
    Label1 = V10,
    Label2 = V11,
    Label3 = V12,
    Matching = V14,
    ACC = V15,
    RT_ms = V16,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Shape = case_when(
      Shape == "shape1.jpg" ~ Label1,
      Shape == "shape2.jpg" ~ Label2,
      Shape == "shape3.jpg" ~ Label3,
    ),
    Identity = case_when(
      Shape == "You" ~ "Self",
      Shape == "none" ~ "None",
      TRUE ~ "Friend"
    ),
    Matching = case_when(
      Matching == 1 ~ "Matching",
      Matching == 2 ~ "Nonmatching"),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "None")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[33] <- "Paper t9 Exp 2"
summary(df[[33]])
```

# Paper t9
## Experiment 3 (Identtiy = 3)
"Self", "Friend", "None"
```{r}
###############################Save Raw Data####################################
# 获取文件列表
file_list <- list.files(
  path = "../4_Data_Extraction/4_2_Open_Data/Paper_t9/Source/Data - Experiment 3/",
  pattern = "^SelfPriorExp_2.*\\.dat$",
  full.names = TRUE
)

# 读取dat文件并存入list中
data_list <- lapply(file_list, read.table, header = FALSE, sep = " ")

combined_data <- do.call(rbind, data_list)

write.csv(
  x = combined_data, 
  file = "../4_Data_Extraction/4_2_Open_Data/Paper_t9/Pt9_Exp3_raw.csv",
  row.names = FALSE
)

rm(file_list, data_list, combined_data)

##################################Clean Data####################################

df[[34]] <- read.csv("../4_Data_Extraction/4_2_Open_Data/Paper_t9/Pt9_Exp3_raw.csv") %>%
  dplyr::select(
    Subject = V1,
    Shape = V7,
    Label1 = V10,
    Label2 = V11,
    Label3 = V12,
    Matching = V14,
    ACC = V15,
    RT_ms = V16,
  ) %>%
  dplyr::mutate(
    Session = 1,
    Shape = case_when(
      Shape == "shape1.jpg" ~ Label1,
      Shape == "shape2.jpg" ~ Label2,
      Shape == "shape3.jpg" ~ Label3,
    ),
    Identity = case_when(
      Shape == "You" ~ "Self",
      Shape == "none" ~ "None",
      TRUE ~ "Friend"
    ),
    Matching = case_when(
      Matching == 1 ~ "Matching",
      Matching == 2 ~ "Nonmatching"),
    RT_ms = as.numeric(RT_ms),
    RT_sec = RT_ms / 1000,
  ) %>%
  dplyr::mutate(
    Subject = as.numeric(Subject),
    Matching = factor(
      Matching, levels = c("Matching", "Nonmatching")
    ),
    Identity = factor(
      Identity, levels = c("Self", "Friend", "None")
    ),
    Session = as.factor(Session),
    RT_ms = as.numeric(RT_ms),
    RT_sec = as.numeric(RT_sec),
    ACC = as.numeric(ACC),
  ) %>%
  dplyr::select(
    Subject, Matching, Identity, Session, RT_ms, RT_sec, ACC
  ) %>%
  dplyr::mutate(
    RT_sec = round(RT_sec, 3),
    RT_ms = round(RT_ms, 0)
  ) %>%
  dplyr::filter(
    RT_sec >= 0.2 & RT_sec <= 1.5,
    ACC == 1 | ACC == 0
  ) %>%
  dplyr::arrange(
    Subject, Matching, Identity, Session
  )

names(df)[34] <- "Paper t9 Exp 3"
summary(df[[34]])
```
