---
title: "3_Reliability"
author: "yuki"
date: "2023-04-30"
output: html_document
---
# Create NULL List
```{r Create NULL List}
res <- list()
```

# First-Second, Odd-Even, Permuted
```{r Name Self - Friend}
res[[1]] <- list()
names(res)[1] <- "Normal SHR"
```

```{r nmshr one by one, message=FALSE, warning=FALSE}
Start_Time <- Sys.time()
df_rt <- yukiBP::shr(list = shl[1:2], Target = c("Self", "Friend", "Stranger"), Paper_ID = "P0S1", Indice = "rt", mc = FALSE, nc = 8) # nolint
df_acc <- yukiBP::shr(list = shl[1:2], Target = c("Self", "Friend", "Stranger"), Paper_ID = "P0S1", Indice = "acc", mc = FALSE, nc = 8) # nolint
df_dp <- yukiBP::shr(list = shl[1:2], Target = c("Self", "Friend", "Stranger"), Paper_ID = "P0S1", Indice = "dp", mc = FALSE, nc = 8) # nolint
df_eff <- yukiBP::shr(list = shl[1:2], Target = c("Self", "Friend", "Stranger"), Paper_ID = "P0S1", Indice = "eff", mc = FALSE, nc = 8) # nolint
df_ezddm <- yukiBP::shr(list = shl[1:2], Target = c("Self", "Friend", "Stranger"), Paper_ID = "P0S1", Indice = "ezddm", mc = FALSE, nc = 8) # nolint
df_rwddm <- yukiBP::shr(list = shl[1:2], Target = c("Self", "Friend", "Stranger"), Paper_ID = "P0S1", Indice = "rwddm", mc = FALSE, nc = 8) # nolint
End_Time <- Sys.time()
```

```{r Rbind 6 Indices}
res[[1]] <- rbind(df_rt, df_acc, df_dp, df_eff, df_ezddm, df_rwddm) %>%
  dplyr::mutate(
    Indice = case_when(
      Indice == "rt" ~ "RT",
      Indice == "acc" ~ "ACC",
      Indice == "dp" ~ "d Prime",
      Indice == "eff" ~ "Efficiency",
      Indice == "ez_v" ~ "ezDDM v",
      Indice == "ez_z" ~ "ezDDM z",
      Indice == "rw_v" ~ "rwDDM v",
      Indice == "rw_z" ~ "rwDDM z",
    )
  ) %>%
  dplyr::mutate(
    Indice = factor(
      Indice, levels = c(
        "RT", "ACC", "d Prime", "Efficiency",
        "ezDDM v", "ezDDM z", "rwDDM v", "rwDDM z"
      )
    ),
    Method = factor(
      Method, levels = c("First-Second", "Odd-Even", "Permuted")
    ),
    Target = factor(Target),
  ) %>%
  dplyr::select(
    Target, Indice, Method, r, Paper_ID
  ) %>%
  dplyr::arrange(
    Target, Indice, Method
  )

rm(df_rt, df_acc, df_dp, df_eff, df_ezddm, df_rwddm)
```

```{r Save nmshr}
write.csv(x = res[[1]], file = "./OUTPUT/nmshr_P0S1.csv", row.names = FALSE)
```

df[[1]]   "P0E1"    "Self", "Friend", "Stranger"
df[[2]]   "P6E1"    "Self", "Partner", "Stranger"
df[[3]]   "P46E2"    "Self", "Stranger"
df[[4]]   "P51E1"   "Self", "Celebrity", "Stranger"
df[[5]]   "P51E2"   "Self", "Celebrity"
df[[6]]   "P54E1"   "Self", "Mother","none", "Acquaintance"
df[[7]]   "P54E3"   "Self", "Mother", "Acquaintance"
df[[8]]   "Pn4E1"   "Self", "Friend", "Stranger"
df[[9]]   "Pn13E1"   "Self", "Friend", "Stranger"
df[[10]]   "Pn13E3"   "Self", "Father", "Stranger"
df[[11]]   "Pn13E4"   "Self", "Friend", "Stranger"
df[[12]]   "Pn16E1"   "Self", "Friend"
df[[13]]   "Pn16E2"   "Self", "Friend"
df[[14]]   "Pn16E3"   "Self", "Friend"
df[[15]]   "Pn23E1"   "Self", "Friend", "Stranger"
df[[16]]   "P95E1"   "Self", "Friend", "Stranger"
df[[17]]   "P95E2"   "Self", "Friend", "Stranger"
df[[18]]   "Ps1E1"    "Self", "Stranger"


################################################################################
--------------------------------------------------------------------------------
################################################################################

# Permuted
```{r Name Self - Friend}
res[[2]] <- list()
names(res)[2] <- "Permuted SHR"
```

```{r mcshr one by one, message=FALSE, warning=FALSE}
Start_Time <- Sys.time()
df_rt <- yukiBP::shr(list = shl[[3]], Target = c("Self", "Friend", "Stranger"), Paper_ID = "P6S1", Indice = "rt", mc = TRUE, nc = 16) # nolint
df_acc <- yukiBP::shr(list = shl[[3]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "acc", mc = TRUE, nc = 16) # nolint
df_dp <- yukiBP::shr(list = shl[[3]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "dp", mc = TRUE, nc = 16) # nolint
df_eff <- yukiBP::shr(list = shl[[3]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "eff", mc = TRUE, nc = 16) # nolint
df_ezddm <- yukiBP::shr(list = shl[[3]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "ezddm", mc = TRUE, nc = 16) # nolint
RWiener_Time <- Sys.time()
df_rwddm <- yukiBP::shr(list = shl[[3]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "rwddm", mc = TRUE, nc = 16) # nolint
End_Time <- Sys.time()
```

```{r Rbind 6 Indices}
res[[2]] <- rbind(df_rt, df_acc, df_dp, df_eff, df_ezddm, df_rwddm) %>%
  dplyr::mutate(
    Indice = case_when(
      Indice == "rt" ~ "RT",
      Indice == "acc" ~ "ACC",
      Indice == "dp" ~ "d Prime",
      Indice == "eff" ~ "Efficiency",
      Indice == "ez_v" ~ "ezDDM v",
      Indice == "ez_z" ~ "ezDDM z",
      Indice == "rw_v" ~ "rwDDM v",
      Indice == "rw_z" ~ "rwDDM z",
    )
  ) %>%
  dplyr::mutate(
    Indice = factor(
      Indice, levels = c(
        "RT", "ACC", "d Prime", "Efficiency",
        "ezDDM v", "ezDDM z", "rwDDM v", "rwDDM z"
      )
    ),
    Target = factor(Target),
   ) %>%
  dplyr::select(
    Target, Indice, r, LLCI, ULCI, Paper_ID
  ) %>%
  dplyr::arrange(
    Target, Indice
  )

rm(df_rt, df_acc, df_dp, df_eff, df_ezddm, df_rwddm)
```

```{r Save mcshr_friend}
write.csv(x = res[[2]], file = "./OUTPUT/pershr_P0S1.csv", row.names = FALSE)
```

df[[1]]   "P0E1"    "Self", "Friend", "Stranger"
df[[2]]   "P6E1"    "Self", "Partner", "Stranger"
df[[3]]   "P46E2"    "Self", "Stranger"
df[[4]]   "P51E1"   "Self", "Celebrity", "Stranger"
df[[5]]   "P51E2"   "Self", "Celebrity"
df[[6]]   "P54E1"   "Self", "Mother","none", "Acquaintance"
df[[7]]   "P54E3"   "Self", "Mother", "Acquaintance"
df[[8]]   "Pn4E1"   "Self", "Friend", "Stranger"
df[[9]]   "Pn13E1"   "Self", "Friend", "Stranger"
df[[10]]   "Pn13E3"   "Self", "Father", "Stranger"
df[[11]]   "Pn13E4"   "Self", "Friend", "Stranger"
df[[12]]   "Pn16E1"   "Self", "Friend"
df[[13]]   "Pn16E2"   "Self", "Friend"
df[[14]]   "Pn16E3"   "Self", "Friend"
df[[15]]   "Pn23E1"   "Self", "Friend", "Stranger"
df[[16]]   "P95E1"   "Self", "Friend", "Stranger"
df[[17]]   "P95E2"   "Self", "Friend", "Stranger"
df[[18]]   "Ps1E1"    "Self", "Stranger"

################################################################################
--------------------------------------------------------------------------------
################################################################################

# Monte Carlo
```{r Name Self - Friend}
res[[3]] <- list()
names(res)[3] <- "Monte-Carlo SHR"
```

```{r mcshr one by one, message=FALSE, warning=FALSE}
Start_Time <- Sys.time()
df_rt <- yukiBP::shr(list = shl[[4]], Target = c("Self", "Friend", "Stranger"), Paper_ID = "P6S1", Indice = "rt", mc = TRUE, nc = 16) # nolint
df_acc <- yukiBP::shr(list = shl[[4]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "acc", mc = TRUE, nc = 16) # nolint
df_dp <- yukiBP::shr(list = shl[[4]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "dp", mc = TRUE, nc = 16) # nolint
df_eff <- yukiBP::shr(list = shl[[4]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "eff", mc = TRUE, nc = 16) # nolint
df_ezddm <- yukiBP::shr(list = shl[[4]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "ezddm", mc = TRUE, nc = 16) # nolint
RWiener_Time <- Sys.time()
df_rwddm <- yukiBP::shr(list = shl[[4]], Target = c("Self", "Partner", "Stranger"), Paper_ID = "P6S1", Indice = "rwddm", mc = TRUE, nc = 16) # nolint
End_Time <- Sys.time()
```

```{r Rbind 6 Indices}
res[[3]] <- rbind(df_rt, df_acc, df_dp, df_eff, df_ezddm, df_rwddm) %>%
  dplyr::mutate(
    Indice = case_when(
      Indice == "rt" ~ "RT",
      Indice == "acc" ~ "ACC",
      Indice == "dp" ~ "d Prime",
      Indice == "eff" ~ "Efficiency",
      Indice == "ez_v" ~ "ezDDM v",
      Indice == "ez_z" ~ "ezDDM z",
      Indice == "rw_v" ~ "rwDDM v",
      Indice == "rw_z" ~ "rwDDM z",
    )
  ) %>%
  dplyr::mutate(
    Indice = factor(
      Indice, levels = c(
        "RT", "ACC", "d Prime", "Efficiency",
        "ezDDM v", "ezDDM z", "rwDDM v", "rwDDM z"
      )
    ),
    Target = factor(Target),
   ) %>%
  dplyr::select(
    Target, Indice, r, LLCI, ULCI, Paper_ID
  ) %>%
  dplyr::arrange(
    Target, Indice
  )

rm(df_rt, df_acc, df_dp, df_eff, df_ezddm, df_rwddm)
```

```{r Save mcshr_friend}
write.csv(x = res[[3]], file = "./OUTPUT/mcshr_P0S1.csv", row.names = FALSE)
```
df[[1]]   "P0E1"    "Self", "Friend", "Stranger"
df[[2]]   "P6E1"    "Self", "Partner", "Stranger"
df[[3]]   "P46E2"    "Self", "Stranger"
df[[4]]   "P51E1"   "Self", "Celebrity", "Stranger"
df[[5]]   "P51E2"   "Self", "Celebrity"
df[[6]]   "P54E1"   "Self", "Mother","none", "Acquaintance"
df[[7]]   "P54E3"   "Self", "Mother", "Acquaintance"
df[[8]]   "Pn4E1"   "Self", "Friend", "Stranger"
df[[9]]   "Pn13E1"   "Self", "Friend", "Stranger"
df[[10]]   "Pn13E3"   "Self", "Father", "Stranger"
df[[11]]   "Pn13E4"   "Self", "Friend", "Stranger"
df[[12]]   "Pn16E1"   "Self", "Friend"
df[[13]]   "Pn16E2"   "Self", "Friend"
df[[14]]   "Pn16E3"   "Self", "Friend"
df[[15]]   "Pn23E1"   "Self", "Friend", "Stranger"
df[[16]]   "P95E1"   "Self", "Friend", "Stranger"
df[[17]]   "P95E2"   "Self", "Friend", "Stranger"
df[[18]]   "Ps1E1"    "Self", "Stranger"